Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-04-29 paper/ms.tex
minor updates
added spatial distribution plot in the paper

\subsubsection{Models with the highest success rates}
\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a mininium number of mock survey
  realizations that are consistent with observations.
  \label{figure:high_success_rate}.}  
\end{figure*}

@@

In Figure XX we present the locii of these models in the parameter
space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$.

@@

>>>>

\subsubsection{Models with the highest success rates}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
\end{center} 
\caption{ Number of models with a mininium number of mock survey
  realizations that are consistent with observations.
  \label{figure:high_success_rate}.}  
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
\end{center} 
\caption{Spatial distribution for two mocks corresponding to the model
  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
  different mock  surveys for this model in the {\texttt match}
  configuration are consistent with observations at the $P>0.05$
  level. The full data for all the mocks can be found in the github
  repository for this paper.
  \label{figure:spatial_distro}.}
\end{figure*}

@@

In Figure XX we present the locii of these models in the parameter
space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$. In
Figure XX we show the spatial distribution for two mock surveys
corresponding to one of such models.

@@

lun abr 29 07:38:58 COT 2013
